---
title       : Reproducible Pitch Presentation
subtitle    : 
author      : Huang Lin
job         : Xiamen University, Fujian, China
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Slide 1

- This is the Course Project of Developing Data Products: Shiny Application and Reproducible Pitch.
- This app is a simple extension of example from Shiny tutorial. We have some data, one variable( Waiting time to next eruption (in mins) ) from Old Faithful Geyser Data.

--- .class #id 

## Slide 2

Use numericInput to set number of bars of histogram
```{r echo=TRUE}
library(manipulate)
myHist <- function(num){
  hist(faithful[,2],col="blue",breaks=num)
}
manipulate(myHist(num), num = slider(1, 100, step = 5))
```

--- .class #id 

## Slide 3

Use sliderInput to set color of bars
```{r echo=TRUE}
library(manipulate)
myHist <- function(color){
  hist(faithful[,2],col=color,breaks=10)
}
manipulate(myHist(color), color = slider(1, 8, step = 1))
```

--- .class #id 

## Slide 4

After setting these two parameters you see the values in table under the graph.

--- .class #id

## Slide 5

Thank You for Viewing

--- .class #id 



